Run the model

### 2019-05-14 scripts/model/1_checks.Rmd
Updated scripts tha generate a couple of figures

# Model description

We model the PNA as a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure. Patches 2-9 are the other PNA countries, and Patch 10 represents the high seas and non-PNA countries. The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually. The price of fish is $p$, and catchability is given by $q$.

In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period. The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions. Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$). Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season. In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$. The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:

$$
\begin{align}
\Pi_1(E_1,X_1,R) = pqE_1X_1(\theta + (1 - \theta)(1 - R))-cE_1^\beta
\end{align}
$$

And profits from fishing in Patch $j = \{2, 3, ..., 10\}$ are:

$$
\begin{align}
\Pi_j(E_j,X_j) = pqE_jX_j-cE_j^\beta
\end{align}
$$

@@

$$
\begin{align}
\pi_1(E_1) = pqX_1(\theta + (1 - \theta)(1 - R)) - \beta cE_1^{\beta-1}
\label{eqn:marginal_profit_1}
\\
\pi_j(E_j) = pqX_j - \beta cE_j^{\beta-1}
\label{eqn:marginal_profit_j}
\end{align}
$$

In practice, the effort levels in each PNA patch are given (so $E_{1},\ E_{2},...,E_{9}$ are given) and the effort level on the high seas ($E_{10}$) is a result of open access dynamics. Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$. Setting Equation \ref{eqn:marginal_profit_j} equal to zero and solving for $E_j$ gives:

$$
\begin{align}
E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
\label{eqn:effort_hs}
\end{align}
$$

The patch-level harvest is then determined by effort and stock size:

$$
\begin{align}
H_1 = qE_1X_1 (\theta + (1 - \theta)(1 - R))
\label{eqn:harvest_1}
\\
H_j = qE_jX_j
\label{eqn:harvest_j}
\end{align}
$$

Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$. The entire stock then grows according to:

$$
\begin{align}
X_{t+1} = e_t + \frac{(\phi + 1)}{\phi}ge_t\left(1 - \left(\frac{e_t}{K}\right) ^{\phi}\right)
\label{eqn:grow}
\end{align}
$$

@@

$$
\begin{align}
X_{it+1} = f_iX_{t+1}
\label{eqn:disperse}
\end{align}
$$

The vessel-day price that a country charges is given by $\pi_i$ from Equations \ref{eqn:marginal_profit_1} and \ref{eqn:marginal_profit_j}. Therefore, patch-level license revenues are given by:

$$
\begin{align}
\omega = \pi_iE_i
\label{eqn:license_revenue}
\end{align}
$$

Equations \ref{eqn:harvest_1} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches. But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents. Thus, the spillover benefits of increasing $R$ are never completely captured.

The vessel-day price for parcels that do not implement a reserve ($j = c(2, 10)$) is given by:

$$
\pi(E_j) = pqX_j - \beta c E_j ^{\beta - 1}
$$

We can solve for $E_j$:

$$
\begin{split}
\pi_j + \beta c E_j ^{\beta - 1} &= pqX_j \\
\beta c E_j ^{\beta - 1} &= pqX_j - \pi_j \\
E_j ^{\beta - 1} &= \frac{pqX_j - \pi_j}{\beta c } \\
E_j &= \left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1}}
\end{split}
$$

For the parcel that implements the reserve ($i = 1$) the same equations are given by:

$$
\pi_1(E_1) = pqX_1 (\theta + (1 - \theta)(1 - R))- \beta c E_1 ^{\beta - 1}
$$

For simplicity, we can write $\Omega = (\theta + (1 - \theta)(1 - R))$, and the baove becomes

$$
\pi_1(E_1) = pqX_1\Omega - \beta c E_1 ^{\beta - 1}
$$

We can solve for $E_i$ as in the previous casse:

$$
\begin{split}
\pi_1 + \beta c E_1 ^{\beta - 1} &= pqX_1\Omega \\
\beta c E_1 ^{\beta - 1} &= pqX_1\Omega - \pi_1 \\
E_1 ^{\beta - 1} &= \frac{pqX_1\Omega - \pi_1}{\beta c} \\
E_1 &= \left(\frac{pqX_1\Omega - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
\end{split}
$$

The total vessel-days for cells that belong to PNA countries (*i.e.* i = (1, 9)) are constrained at 45,000, which we term $\bar{E}$. Therefore, total effort can be expressed as:

$$
\bar{E} = \left(\frac{pqX_1(\theta + (1 - \theta)(1 - R)) - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}} + 
\sum_{j = 2}^9\left(\frac{pqX_j - \pi_j}{\beta c }\right) ^ { \frac{1}{\beta - 1} }
$$

This parameterization shows that the cell-level effort is determined by the combination of stock size ($X_j$) and the price $\pi$. Trading between country will continue until all $\pi_i$ reach an equilibrium price of $\bar{\pi}$.

>>>>

#Model for marine conservation with effort markets

We model a ten-patch discrete-time meta-population system, where Patch 1 is considering a spatial closure. Patches 1 - 9 opperate under a vessel-day schemePatches, and Patch 10 represents the high seas and other areas not managed under a VDS. The stock of fish in each country is relatively stationary within a single fishing season, but redistributes across all patches annually. The price of fish is $p$, and catchability is given by $q$. These parameters are held constant across patches.

##Fishery dynamics

In the absence of a reserve, the revenue for vessels in patch $i$ is given by $pqE_iX_i$, where $E_i$ and $X_i$ are effort (vessel-days) and stock size in patch $i$ at the beginning of a period. The cost of fishing in patch $i$ is given by $cE_i^\beta$, where $\beta = 1.3$ matches commonly-used cost functions.

Patch 1 considers a spatial closure by implementing a reserve as a fraction $R$ of the total patch ($R \in[0,1)$). Fish move within a patch based on $\theta$, where $\theta = 0$ implies no movement within the patch, and $\theta = 1$ implies that fish within the patch are well mixed during the fishing season. In this patch, revenues are given by $pqE_1X1(\theta + (1 - \theta)(1 - R))$. The parameterization of movement and reserve size imply that profit from fishing Patch 1 is given by:

$$
\Pi_1(E_1,X_1,R) = pqE_1X_1\Omega_i-cE_1^\beta
$$

With $\Omega_i = (\theta + (1 - \theta)(1 - R))$ being a parameterization that combines reserve size as a proportion of patch ($R =  (0, 1)$) and within-patch fish movement ($\theta$). Under this parameterization, $\Omega_{i \not 1} = 1$ since only Patch 1 implements a reserve.

Profits from fishing in each Patch are:

$$
\Pi_i(E_i,X_i) = pqE_iX_i\Omega_i-cE_i^\beta
$$

@@

$$
\pi_1(E_1) = pqX_1\Omega_i - \beta cE_1^{\beta-1}
\label{eqn:marginal_profit}
$$

In practice, the effort levels in each Patch are allocated by management (so $E_{1},\ E_{2},...,E_{9}$ are given) and the
effort level on the high seas ($E_{10}$) is a result of open access dynamics. Therefore, we assume that effort continues to enter Patch 10 until the profit from the last unit of effort is exactly zero, indicating that $E_{10}$ is the value for which $\pi_{10}(E_{10})  = 0$. Setting Equation \ref{eqn:marginal_profit} for $i = 10$ equal to zero and removing $\Omega_{10} = 1$ for simplicity, we can solve for $E_{10}$:

$$
E_{10} = \left(\frac{pqX_{10}}{\beta c}\right)^{\frac{1}{(\beta - 1)}}
\label{eqn:effort_hs}
$$

Under vds-operated patches, however, profits from marginal effort must equate the cost of fishing in the patch. Therefore vessel-day price for patches under vds ($i = (1, 9)$) is  given by:

$$
\pi(E_i) = pqX_i\Omega_i - \beta c E_i ^{\beta - 1}
$$

We can solve for $E_i$ and obtain:

\begin{equation}
	\begin{split}
		\pi_i + \beta c E_i ^{\beta - 1} &= pqX_i\Omega_i \\
		\beta c E_i ^{\beta - 1} &= pqX_i\Omega_i - \pi_i \\
		E_i ^{\beta - 1} &= \frac{pqX_i\Omega_i - \pi_1}{\beta c} \\
		E_i &= \left(\frac{pqX_i\Omega_i - \pi_1}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
	\end{split}
\label{eqn:demands}
\end{equation}

Therefore, total allowable effort in the fishery is given by:

$$
\bar{E} = \sum_{i = 1}^9\left(\frac{pqX_i\Omega_i - \pi}{\beta c }\right) ^ {\frac{1}{\beta - 1}}
\label{eqn:Ebar}
$$

## Stock dynamics

Patch-level harvest is then determined by effort and stock size:

$$
H_i = qE_iX_i\Omega_i
\label{eqn:harvest}
$$

Therefore, escapement in patch $i$ is the difference between initial stock size and harvests given by $e_{it} = X{it} - H_{it}$ and total escapement is $e_t=\sum_{i=1}^{10}e_{it}$. The entire stock then grows logistically according to:

$$
X_{t+1} = e_t + e^{r \times \frac{e}{K}}
\label{eqn:grow}
$$

Where $r$ and $K$ are species-specific intrinsic growth rate and carrying capacity.

@@

$$
X_{it+1} = f_iX_{t+1}
\label{eqn:disperse}
$$

## Vessel-day revenues

The vessel-day price that a country charges is given by $\pi_i$ from Eqn \ref{eqn:marginal_profit}. Therefore, patch-level license revenues are given by:

$$
\omega = \pi_iE_i
\label{eqn:license_revenue}
$$

Equation \ref{eqn:harvest} shows that low values of $\theta$ and $R > 0$ would increase escapement, which would lead to an increase in stock size (Equation \ref{eqn:grow}) and a benefit to all the other patches. But this would also cause the stock in the high seas ($X_{10}$) to increase, leading to an increased effort being allocated to the high seas (Equation \ref{eqn:effort_hs}) and a loss of these potential rents. Thus, the spillover benefits of increasing $R$ are never completely captured.

## Allocation rules

In the second scenario above, effort from a patch with conservation is traded to other patches. This means that its allocation will decrease as purse seine effort in its EEZ is reduced. After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time. At the end of every time, vessel-days are allocated to each patch based on the following rule:

$$
E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
$$

Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$). We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures. The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales. We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).

### 2019-05-14 scripts/model/2_run_model.Rmd
Updated scripts tha generate a couple of figures

---
title: "Run the model"
author: "Villaseñor-Derbez J.C."
date: "Updated on `r Sys.Date()`"
output:
  html_document: 
    code_folding: show
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: false
---

@@

## Define parameters

@@

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue
  )
```

@@

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Costs (% of case with no reserve)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue
  )
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with no reserve)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided by trading") +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.position = "None"))
```

@@

```{r, fig.width = 4, fig.height = 7}
(cost_plot <- cowplot::plot_grid(costs_no_trading_plot,
                   costs_with_trading_plot,
                   delta_costs_plot, ncol = 1))
```

@@

```{r}
ggsave(plot = cost_plot,
       filename = here("docs", "img", "cost_plot.pdf"), width = 4, height = 7)
```

@@

```{r}
DF_results_no_trading %>% 
  filter(!Country == "HS") %>% 
  mutate(Country = fct_relevel(Country, "KIR")) %>% 
  ggplot() +
  geom_line(aes(
    x = R,
    y = VDSprice,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-day Price ("~pi~")")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black")) +
  facet_wrap(~Country, scales = "free_y")
```

@@

```{r}
ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = VDSprice,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-day Price ("~pi~")")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black"))
```

## Where do vessels go?

@@

```{r}
DF_results_no_trading %>% 
  filter(!Country == "HS") %>%
  mutate(Country = fct_relevel(Country, "KIR")) %>% 
  ggplot() +
  geom_line(aes(
    x = R,
    y = Vessel_Days,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab(quo("Vessel-Days")) +
  scale_color_viridis_c() +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                ticks.colour = "black",
                                frame.colour = "black")) +
  facet_wrap(~Country, scales = "free_y")
```

>>>>

---
title: "Run the model"
author: "Villaseñor-Derbez J.C."
date: "Updated on `r Sys.Date()`"
output:
  html_document: 
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: false
---

@@

## Description of simulations

We inform our model to losely match the fishery dynamics observed for the VDS operated by the PNA. The table below contains the values used to parameterize the model.

### Define parameters

@@

### Create and export a table of parameters and sources

```{r}
params <- tibble(
  parameter = c(
    "MSY",
    "$B_{msy}$",
    "K",
    "$B_c/B_{msy}$",
    "$C_{now}$",
    "$B_{now}$",
    "$r$",
    "$\\beta$",
    "p",
    "q",
    "c",
    "f"
  ),
  value = c(MSY, Bmsy, K, Bc_B0, Cnow, Bnow, r, beta, p, q, c, 0.1),
  source = c(
    "50th percentile from MSY in table 8 of Stock Assessment",
    "50th percentile from MSY in table 8 of Stock Assessment",
    "50th percentile from MSY in table 8 of Stock Assessment",
    "50th percentile from MSY in table 8 of Stock Assessment",
    "Catches from Stock Assessment",
    "Current Biomass (2012 - 2015 average)",
    "From fishbase: Prior r = 0.57, 95 CL = 0.41 - 0.78",
    "Standard",
    "Mean between Thailand and Japan values (Value of WCPFC-CA tuna fisheries 2017 report)",
    "Estimated so that efforts match catches given biomass and vessel-day prices",
    "-",
    "Biomass is equally distributed between patches ($f_i = 0.1$)"

  )
)

params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"), format = "latex", escape = F) %>% 
  cat(file = here("docs", "tab", "parameters.tex"))
```

We use the model above run three different simulations. We test the model across a range reserve sizes and movement parameters. We use to main scenarios. The first scenario does not allow trading. In this case, total allowable effort ($\bar{E}$) and biomass $B_{now}$ are known and equally distributed among patches 1-9. For patch 10, we solve for Ei until biomass converges to match $B_{now}$. We then proceed to ``close'' a portion of Patch 1, and calculate the vessel-day price in Patch 1 given that only $X_i\Omega_i$ biomass is available for harvest. We compare vessel-day revenues of each scenario to a case with no reserve ($R = 0$). This produces a measure of the cost of implementing a spatial closure of size $R$ in patch 1.

The second scenario allows trading. We start again by solving for the high seas to obtain total effort. Since a closure is not in effect, this equiulibrium is the same as the first step above. We then implement a spatial closure in patch 1. This essentially lowers the price fishers would be willing to pay to fish in a patch with biomass $X_i\Omega_i$, lowering demand for vessel-days in pach 1. Patches 2 - 9 have a higher demand for vessel days, and therefore a portion of vessel-days from patch 1 are sold to patches 2 - 9. This increases effort in these patches, which reduces escapement and therefore biomass. This reduction in biomass in turn would modify the demand curves (Ei). We therefore iterate this process until biomass stabilizes, therefore finding the system's equilibrium. Like before, we calculate vessel-day revenues to each patch and compare them to a case with no reserve in patch 1.

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
  )
```

@@

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Costs\n(% of case with R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
  )
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs (% of case with R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot_long_axis,
       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
       width = 3,
       height = 3)
```

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs\n(% of case with R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  theme(legend.position = "None"))
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  theme(legend.position = "None"))
```

@@

```{r, fig.width = 4, fig.height = 7}
(cost_plot <- plot_grid(costs_no_trading_plot,
                        costs_with_trading_plot,
                        delta_costs_plot,
                        ncol = 1,
                        labels = "AUTO"))
```

@@

```{r}
ggsave(plot = cost_plot,
       filename = here("docs", "img", "PNA_model.pdf"),
       width = 3.4,
       height = 7)
```

@@

```{r}
country_anom <- tibble(Country = c("KIR", "FSM", "MHL", "NRU", "PLW", "PNG", "SLB", "TKL","TUV","HS"),
                       Country_a = 1:10)

(vessel_day_price_no_trading_plot <- 
    DF_results_no_trading %>%
    left_join(country_anom, by = "Country") %>% 
    filter(Country_a %in% c(1, 2)) %>% 
    mutate(Country_a = ifelse(Country_a == 1, "Patch 1", "Patches 2 - 9"),
           Country_a = fct_relevel(Country_a, "Patch 1")) %>% 
    ggplot(aes(x = R, y = VDSprice, color = theta, group = theta)) +
    geom_line(size = 1) +
    facet_wrap( ~ Country_a, scale = "free_y") +
    xlab("Portion of patch as reserve (R)") +
    ylab("Vessel-day price") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black"))+
    theme(legend.position = c(0.6, 1),
          legend.justification = c(0, 1)))
```

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       filename = here("docs", "img", "vessel_day_price_no_trading_plot.pdf"),
       width = 6,
       height = 3)
```

@@

```{r}
(vessel_day_price_with_trading_plot <- ggplot(data = DF_1_with_trading) +
   geom_line(aes(
     x = R,
     y = VDSprice,
     group = theta,
     color = theta
   ),
   size = 1
   ) +
   xlab("Portion of patch as reserve (R)") +
   ylab(quo("Vessel-day Price ("~pi~")")) +
   scale_color_viridis_c() +
   theme(
     text = element_text(size = 10),
     axis.text = element_text(size = 8)
   ) +
   startR::ggtheme_plot() +
   guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black")))
```

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       filename = here("docs", "img", "vessel_day_price_with_trading_plot.pdf"),
       width = 6,
       height = 4.5)
```

## What about revenue to other PNA countries?

@@

```{r}
(
  profits_PNA_notKIR_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost_pna_not_kir,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Additional profits (% of case with R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1))
)
```

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot.pdf"),
       width = 3,
       height = 3)
```

# Allocation rules matter

## Allocation rules

In the second scenario above, effort from a patch with conservation is traded to other patches. This means that its allocation will decrease as purse seine effort in its EEZ is reduced. After solving for the new equilibrium for each combination of $R$ and $\theta$, we project the fishery 50 years in time. At the end of every time, vessel-days are allocated to each patch based on the following rule:

$$
E_i^* = \alpha \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}E_{i,t-\tau}}{\bar{E}\hat{\tau}} \right) +
(1 - \alpha) \left(\frac{\sum_{\tau = 0}^{\hat{\tau}}X_{i,t-\tau}}{\bar{X}\hat{\tau}} \right)
$$

Where  $\alpha$ is a weight on historical effort ($E_i$) and $1-\alpha$ is the weight in historical biomass ($B_i$). We use $\hat{\tau}= 7$ to obtain a moving mean of 7 years for these measures. The difference between allocated days ($E_i^*$) and used days (determined by Eq: \ref{eqn:demands}) for patch 1 are the sales. We then calculate vessel-day revenues to each country over the 50-year time horizon and compare them to a case where there is no reserve and allocations are based solely on biomass ($\alpha = 0$).

```{r}
source(here("scripts", "model", "allocate.R"))
source(here("scripts", "model", "allocate_wrap.R"))
source(here("scripts", "model", "move_in_time.R"))
source(here("scripts", "model", "move_in_time_no_trading.R"))
```

We first obtain the optimal allocation by running the model until steady state and with no reserves.

```{r}

alphas <- c(0, 0.25, 0.5, 0.75, 1)

delta <- 1 / 1.1

plan(multiprocess)

allocation <-
  expand.grid(
    R = Rvec,
    theta = c(0.25, 0.5, 0.75),
    alpha = alphas,
    trade = T
  ) %>%
  as_tibble() %>%
  mutate(
    resutls = future_pmap(
      .l = list(
        alpha = alpha,
        R = R,
        theta = theta,
        trade = trade
      ),
      .f = allocate_wrap, 
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest() %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  )

best_rev <- allocate_wrap(
  alpha = 0,
  R = 0,
  theta = 0.5,
  trade = T,
  fvec = fvec,
  r = r,
  K = K,
  p = p,
  q = q,
  Xvec = Xvec,
  beta = beta,
  c = c,
  E = E
) %>%
  filter(country == "KIR") %>%
  mutate(
    rev_dir = Ei * pi,
    deltaE = Ea - Ei,
    rev_sells = deltaE * pi,
    rev_tot = rev_dir + rev_sells,
    fct = delta ^ year,
    rev_tot_disc = rev_tot * fct
  ) %$%
  sum(rev_tot)
```

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Costs\n(% of case with R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 4.5,
  height = 3.5
)
```

```{r}
#Slide export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3
)
```

```{r, eval = F}
allocation %>%
  filter(!trade) %>% 
  ggplot(aes(x = year, y = Ea, color = R, group = paste(alpha, R, theta))) +
  geom_line(size = 1) +
  facet_grid(alpha ~ theta) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```

```{r, eval = F}
allocation %>%
  filter(theta == 0.5, !trade) %>% 
  ggplot(aes(x = year, y = Xi, color = R, group = paste(alpha, R))) +
  geom_line(size = 1) +
  facet_grid(~alpha) +
  scale_color_viridis_c() +
  guides(color = guide_colorbar(ticks.colour = "black", frame.colour = "black")) +
  ggtheme_plot()
```
